A North Sámi to South Sámi machine translation prototype

### 2014-02-08 paper/paper.tex
ref

Norwegian North Germanic. The Saami languages constitute the
westernmost branch of the Uralic language family. They contain most of
the classical Uralic characteristica: A rich verbal morphology (3
numbers and persons, a rich repertoire of infinite forms), and a
medium-size case system with both grammatical and adverbial functions,
and no gender distinction. They also show extensive contact with their
Germanic neighbours. Many grammatical structures are head-initial
constructions, as compared to the classical Uralic pattern, and the
tense system is compatible with the North Germanic one.

@@

@@

\section{Evaluation}
%@ lene,fran
\item translation nob-sma which actually is nob-sme-sma (should somehow be in the title?) 
\item the evaluators evaluate nob-sma

@@

\section{Future work}
%@trond
\section{Conclusions}
%@trond
\item reaction from sma linguist in the normgiving organ: she sees the possibility of using MT as a help for discussing terminology and getting the best ones into use
\item the language socity is used to the impact from the mojority languages, a new controversial(?) thought is the linguistic impact from another minority lanugage

>>>>

Norwegian North Germanic. The Saami languages constitute the
westernmost branch of the Uralic language family. They possess most of
the classical Uralic characteristica: A rich verbal morphology (3
numbers and persons, a rich repertoire of infinite forms), and a
medium-size case system with both grammatical and adverbial functions,
and no gender distinction. They also show extensive contact with their
Germanic neighbours. Many grammatical structures are head-initial
constructions, as compared to the classical Uralic pattern, and the
tense system is compatible with the North Germanic one.

@@

An overview \cite{sammallahti98}.

@@

\section{Evaluation}
%@ lene,fran
 translation nob-sma which actually is nob-sme-sma (should somehow be in the title?) 
 the evaluators evaluate nob-sma

@@

\section{Future work}
%@trond
\section{Conclusions}
%@trond

 reaction from sma linguist in the normgiving organ: she sees the possibility of using MT as a help for discussing terminology and getting the best ones into use

 the language socity is used to the impact from the mojority languages, a new controversial(?) thought is the linguistic impact from another minority lanugage
